---
title: "EDA"
author: "Deepak"
date: "2023-11-25"
output:
  html_document:
    df_print: paged
  pdf_document: default
---


#### 1. First Feel of the data

```{r sepsis_df, include=FALSE}
  library(tidyverse)
  library(skimr)
  library(summarytools)
  sepsis_df <- read_csv("sepsis.csv", show_col_types = F)
```

```{r echo=FALSE}
  head(sepsis_df)
```


```{r sepsis, echo=FALSE}
  str(sepsis_df)
```

## Including Plots

You can also embed plots, for example:

```{r echo=FALSE}
dim(sepsis_df)
```


```{r echo=FALSE}
summary(sepsis_df)
```
So, we have 3 categorical variables and 6 continuous variables.

```{r echo=FALSE}
skim(sepsis_df)
```
```{r echo=FALSE}
skim_without_charts(sepsis_df)
```


```{r echo=FALSE}
dfSummary(sepsis_df) %>%
  view()
```

```{r eval=FALSE, include=FALSE}
vis_dat(sepsis_df)
```
```{r echo=FALSE}
vis_miss(sepsis_df)
```

```{r echo=FALSE}
  select(5,6,8,9)
  head(sepsis_num_df,6)
```

```{r echo=FALSE}
vis_cor(sepsis_num_df)
```

```{r echo=FALSE}
sepsis_df %>%
  ggplot(mapping = aes(x = fate, alpha = 0.1)) +
  geom_bar(fill = "red") +
  theme_minimal()
```

```{r}
View(sepsis_df)
```


```{r eval=FALSE, include=FALSE}
eda_paged_report(sepsis_df, output_format = "pdf")
```

```{r echo=FALSE}
plot_intro(sepsis_df)
```

```{r}
plot_missing(sepsis_df)
```
```{r}
plot_histogram(sepsis_num_df)
```

```{r}
plot_correlation(na.omit(sepsis_df))
```

```{r eval=FALSE, include=FALSE}
create_report(sepsis_df)
```
###### Feature Engineering functions, Transform character based columns into factors

```{r}
sepsis_df %>%
  mutate_if(is.character, as.factor)
```
From dataexplorer, mutate and update to change colum names

```{r}
update_columns(sepsis_df, c("treat", "race"), as.factor)
```
Dummify from dataexplorer package works like spread to change variables from categorical to numerical to replace it with a dummy varialble

```{r}
dummify(sepsis_df) 
#or 
dummify(sepsis_df, select = "treat") #columns to dummify
```


```{r eval=FALSE, include=FALSE}
diagnose_paged_report(sepsis_df, output_format = "pdf") #from dlookr
```

